---
title: "Publications"
format: 
  html:
      page-layout: full
knitr: 
  opts_chunk: 
    dev: [svg, darksvg]
    fig.ext: [.-light.svg, .-dark.svg]
include-after-body:
  text: |
    <script type="application/javascript" src="image-dark-light.js"></script>
editor: visual
editor_options: 
  chunk_output_type: console

---

```{r, echo=FALSE, warning=FALSE, message=F}
# Maj citation
library(rcrossref)
library(rAltmetric)
library(scholar)
library(dplyr)
library(ggplot2)

# function
find_url_rAltmetric<- function(doi_x){
  url_x <- altmetric_data(altmetrics(doi = doi_x,apikey = ""))$details_url
  return(url_x)
}

find_img_rAltmetric<- function(doi_x){
  url_x <- altmetric_data(altmetrics(doi = doi_x,apikey = ""))$images.medium
  return(url_x)
}

# cosmetic
## Dark_mode also for graph (i add image-dark-light.js from https://github.com/quarto-dev/quarto-cli/discussions/5439)
library(ggdark)
library(devoid)
darksvg = function(file, width, height) {
  on.exit({
    ggplot2::reset_theme_settings()
    # invert_geom_defaults()
  }
    )
  theme_set(dark_mode(theme_get()))
  ggsave(filename = file, width = width, height=height, dev='svg', bg = 'transparent')
  void_dev()
}
```

{{< iconify line-md:download-loop width="1.2em" height="1.2em" >}}: Download publication ; {{< iconify line-md link width="1.2em" height="1.2em" >}}: Link of the publication ; <iconify-icon icon="mdi:unlocked-variant-outline" width="1.2em" height="1.2em"  style="color: #58a53b"></iconify-icon>: Open-access articles ; <iconify-icon icon="line-md:cog-loop" width="1.2em" height="1.2em"  style="color: #58a53b"></iconify-icon>: Article under review ; Last update on: **`r Sys.Date()`**

| N°  | Title                                                                                                                                                                                                                                                                                                                                                                                                                                                       | Author                                                                                                                                                                                                                                                                                                              | Years | Journal                     | Citation|Altmetric|
|------------|------------|------------|------------|------------|------------|------------|
| 4   | Decoding the Double Stress Puzzle: Investigating Nutrient Uptake Efficiency and Root Architecture in Soybean under Heat- and Water- Stresses <iconify-icon icon="mdi:unlocked-variant-outline" width="1.2em" height="1.2em"  style="color: #58a53b"></iconify-icon> <iconify-icon icon="line-md:cog-loop" width="1.2em" height="1.2em"  style="color: #58a53b"></iconify-icon>                                                                              | **Corentin Maslard**, Mustapha Arkoun, Fanny Leroy, Sylvie Girodet, Christophe Salon and Marion Prudent                                                                                                                                                                                                             | 2024  | \-                          | \-                                                              |\-|
| 3   | Ectopic expression of the grape hexose transporter VvHT5 restores STP13-deficiency in *Arabidopsis* and promotes fungal resistance to *Botrytis cinerea* </iconify-icon> <iconify-icon icon="line-md:cog-loop" width="1.2em" height="1.2em"  style="color: #58a53b"></iconify-icon>                                                                                                                                                                         | Benoit Monnereau, Cécile Gaillard, **Corentin Maslard**, Pierre-Antoine Noceto, Anne Cantereau, Pierre Coutos-Thévenot and Sylvain La Camera                                                                                                                                                                        | 2024  | \-                          | \-                                                              |\-|
| 2   | Root architecture characterization in relation to biomass allocation and biological nitrogen fixation in a collection of European soybean genotypes [{{< iconify line-md:download-loop width="1.2em" height="1.2em" >}}](media/publications/2.pdf) [{{< iconify line-md link width="1.2em" height="1.2em" >}}](https://doi.org/10.1051/ocl/2021033) <iconify-icon icon="mdi:unlocked-variant-outline" width="1.2em" height="1.2em"  style="color: #58a53b"> | **Corentin Maslard**, Mustapha Arkoun, Christophe Salon and Marion Prudent                                                                                                                                                                                                                                          | 2021  | OCL                         | `r cr_citation_count(doi="10.1051/ocl/2021033")$count`          |<a href= `r find_url_rAltmetric("10.1051/ocl/2021033")` target="_blank"><img src=`r find_img_rAltmetric("10.1051/ocl/2021033")` width="64" height="64"></a>|
| 1   | Pentadecaibins I−V: 15-Residue Peptaibols Produced by a Marine-Derived *Trichoderma* sp. of the *Harzianum* Clade [{{< iconify line-md:download-loop width="1.2em" height="1.2em" >}}](media/publications/1.pdf) [{{< iconify line-md link width="1.2em" height="1.2em" >}}](https://dx.doi.org/10.1021/acs.jnatprod.0c01355)                                                                                                                               | Anne-Isaline van Bohemen, Nicolas Ruiz, Aurore Zalouk-Vergnoux, Aurore Michaud, Thibaut Robiou du Pont, Irina Druzhinina, Lea Atanasova, Soizic Prado, Bernard Bodo, Laurence Meslet-Cladiere, Bastien Cochereau, Franck Bastide, **Corentin Maslard**, Muriel Marchi, Thomas Guillemette and Yves François Pouchus | 2021  | Journal of Natural Products | `r cr_citation_count(doi="10.1021/acs.jnatprod.0c01355")$count` |<a href= `r find_url_rAltmetric("10.1021/acs.jnatprod.0c01355")` target="_blank"><img src=`r find_img_rAltmetric("10.1021/acs.jnatprod.0c01355")` width="64" height="64"></a>|

```{r, eval=F, echo=F}
#see https://github.com/ropensci/rAltmetric
acuna2 <- altmetrics(doi = "10.1051/ocl/2021033",apikey = "") # but i need the api key
acuna1 <- altmetrics(doi = "10.1021/acs.jnatprod.0c01355",apikey = "")
test1=altmetric_data(acuna2)
test1=altmetric_data(acuna1)


find_url("10.1021/acs.jnatprod.0c01355")
altmetric_data(altmetrics(doi = "10.1021/acs.jnatprod.0c01355",apikey = ""))$details_url

# only for ISSN
# install_github("https://github.com/masonrhayes/sciteR")
library(sciteR)

my_issns <- c("1029-8479", "0092-8674", "0028-0836", "0036-8075")

scite_df <- scite(my_issns)
scite_df <- scite("10.1021/acs.jnatprod.0c01355")

find_url_rAltmetric("10.1016/j.plantsci.2018.09.015")
find_img_rAltmetric("10.1016/j.plantsci.2018.09.015")
find_img_rAltmetric("10.1111/pce.13712")
find_url_rAltmetric("10.1111/pce.13712")
find_url_rAltmetric("10.1007/s13593-014-0272-z")
find_url_rAltmetric("10.1038/s41586-023-05791-5")


cr_citation_count(doi="10.1111/pce.13712")


# google scholar 
# https://cran.r-project.org/web/packages/scholar/scholar.pdf (for more information)
id <- get_publications("TsztyiMAAAAJ&hl") 
impact <- get_journalrank(journals=id$journal)

id <- "bg0BZ-QAAAAJ&hl"
authorlist <- scholar::get_publications(id)$autho
author <- scholar::get_profile(id)$name
ids <- c("B7vSqZsAAAAJ", "qj74uXkAAAAJ")
df <- compare_scholar_careers(ids)
format_publications("DO5oG40AAAAJ")
id <- get_publications("bg0BZ-QAAAAJ&hl")
impact <- get_journalrank(journals=id$journal)

predict_h_index("TsztyiMAAAAJ")

id <- get_publications("TsztyiMAAAAJ&hl")
impact <- get_journalrank(journals=id$journal)



get_journalrank("International Journal of Open Source Software and Processes", max.distance = 0.05)

```

::: {.callout-note collapse="true"}
## Learn about these metrics

- Citations are the number of other articles citing this article, calculated by Crossref. [Find more information about Crossref citation counts](https://www.crossref.org/services/cited-by/)
- The Altmetric Attention Score is a quantitative measure of the attention that a research article has received online. Clicking on the donut icon will load a page at altmetric.com with additional details about the score and the social media presence for the given article. Find more information on the [Altmetric Attention Score and how the score is calculated](https://help.altmetric.com/support/solutions/articles/6000233311-how-is-the-altmetric-attention-score-calculated).
:::

```{r, echo=F, warning=FALSE, message=FALSE}
#| layout-nrow: 1
#| fig-align: left
df <-get_citation_history("TsztyiMAAAAJ&hl") %>%  # my_ID (find in URL)
  mutate(Face=ifelse(year==format(Sys.Date(), "%Y"),"bold","plain"))

ggplot(df,aes(x=year,y=cites))+
    geom_bar(stat = "identity", fill = "#40cdf2",alpha=0.8)+
    geom_text(aes(label = cites), hjust = -0.5)+
    labs(
      x = NULL,
      y = "Citation by years"
  )+
  geom_hline(yintercept=0)+
   #scale_y_reverse(expand = expansion(mult = c(.1, 0))) +
   theme(
        panel.background = element_blank(),
        plot.background = element_blank(),   # Remove plot background
        panel.grid = element_blank(), 
        axis.text.y=element_text(size = 12, face = df$Face),
        axis.ticks.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.x = element_text(size = 12)
      )+
    #scale_x_reverse(position = "top")+
  coord_flip() 


```


