---
title: "Publications"
toc: true
toc-location: right
number-sections: false
execute: 
  echo: false
  message: false
  warning: false
format: 
  html:
      page-layout: full
knitr: 
  opts_chunk: 
    dev: [svg, darksvg]
    fig.ext: [.-light.svg, .-dark.svg]
include-after-body:
  text: |
    <script type="application/javascript" src="image-dark-light.js"></script>
editor: visual
editor_options: 
  chunk_output_type: console
---

```{r, echo=FALSE, warning=FALSE, message=F}
source("src.R")
```

::: column-margin
<iconify-icon icon="material-symbols:construction-rounded" width="1.2em" height="1.2em" style="color: #58a53b"></iconify-icon>: Manuscript in preparation\
<iconify-icon icon="line-md:cog-loop" width="1.2em" height="1.2em"  style="color: #58a53b"></iconify-icon>: Article under review\
<iconify-icon icon="mdi:unlocked-variant-outline" width="1.2em" height="1.2em"  style="color: #58a53b"></iconify-icon>: Open-access articles\
{{< iconify line-md link width="1.2em" height="1.2em" >}}: Link of the publication\
{{< iconify line-md:download-loop width="1.2em" height="1.2em" >}}: Download publication\
{{< iconify line-md:github-loop width="1.2em" height="1.2em" >}}: Code & Data\
{{< iconify academicons:biorxiv width="1.2em" height="1.2em" >}}: Biorxiv or pre-print\
{{< iconify academicons:google-scholar width="1.2em" height="1.2em" >}}: Google Scholar\
{{< iconify academicons:researchgate width="1.2em" height="1.2em" >}}: Researchgate\
{{< iconify academicons:hal width="1.2em" height="1.2em" >}}: HAL\
Last update on: **`r Sys.Date()`**
:::

## Working Papers & Papers Under Review

`r make_pub_list(pubs, "working")`

## Peer-reviewed journal articles

`r make_pub_list(pubs, "peer_reviewed")`

## Magazine Publications

`r make_pub_list(pubs, "magazine")`

## Theses

`r make_pub_list(pubs, "theses")`

::: {.callout-note collapse="true"}
## Learn about these metrics

-   Citations are the number of other articles citing this article, calculated by Crossref. [Find more information about Crossref citation counts](https://www.crossref.org/services/cited-by/)
-   The Altmetric Attention Score is a quantitative measure of the attention that a research article has received online. Clicking on the donut icon will load a page at altmetric.com with additional details about the score and the social media presence for the given article. Find more information on the [Altmetric Attention Score and how the score is calculated](https://help.altmetric.com/support/solutions/articles/6000233311-how-is-the-altmetric-attention-score-calculated).
:::

::::: columns
::: {.column width="25%"}
```{r, echo=FALSE, message=FALSE, warning=FALSE}
profile <- get_profile("TsztyiMAAAAJ&hl")
# Updated data
metrics <- data.frame(
  Metric1 = c("H-Index", "Sum of Times Cited", "Publications"),
  Value1 = c(profile$h_index,
             profile$total_cites,
             sum(pubs$category == "peer_reviewed")
             )
)

# Create a 4-column table with custom styling
kable(metrics, col.names = c("", ""), align = "c", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F) %>%
  column_spec(1, bold = TRUE, width = "10em") %>%
  column_spec(2, bold = TRUE, width = "10em") %>%
  row_spec(0, bold = TRUE, color = "white", background = "black") %>%
  row_spec(1:3)
```
:::

::: {.column width="75%"}
```{r, echo=F, warning=FALSE, message=FALSE}
df <-get_citation_history("TsztyiMAAAAJ&hl") %>%  # my_ID (find in URL)
  mutate(Face=ifelse(year==format(Sys.Date(), "%Y"),"bold","plain"))

ggplot(df,aes(x=year,y=cites))+
    geom_bar(stat = "identity", fill = "#2780e3",alpha=0.8, col='black')+
    geom_text(aes(label = cites), hjust = -0.45,size = 4.8)+
    labs(
      x = NULL,
      y = "Citation by years"
  )+
  geom_hline(yintercept=0)+
   #scale_y_reverse(expand = expansion(mult = c(.1, 0))) +
   theme(
        panel.background = element_blank(),
        plot.background = element_blank(),   # Remove plot background
        panel.grid = element_blank(), 
        axis.text.y=element_text(size = 13, face = df$Face),
        axis.ticks.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.x = element_text(size = 15)
      )+
  coord_flip() 
```
:::
:::::

```{r, eval=F, echo=F}

#################### DRAFT ###################
#see https://github.com/ropensci/rAltmetric
acuna2 <- altmetrics(doi = "10.1051/ocl/2021033",apikey = "") # but i need the api key
acuna1 <- altmetrics(doi = "10.1021/acs.jnatprod.0c01355",apikey = "")
test1=altmetric_data(acuna2)
test1=altmetric_data(acuna1)


find_url("10.1021/acs.jnatprod.0c01355")
altmetric_data(altmetrics(doi = "10.1021/acs.jnatprod.0c01355",apikey = ""))$details_url

# only for ISSN
# install_github("https://github.com/masonrhayes/sciteR")
library(sciteR)

my_issns <- c("1029-8479", "0092-8674", "0028-0836", "0036-8075")

scite_df <- scite(my_issns)
scite_df <- scite("10.1021/acs.jnatprod.0c01355")

cr_citation_count(doi="10.1111/pce.13712")


# google scholar 
# https://cran.r-project.org/web/packages/scholar/scholar.pdf (for more information)
id <- get_publications("TsztyiMAAAAJ&hl")
impact <- get_journalrank(journals=id$journal)

id <- "bg0BZ-QAAAAJ&hl"
authorlist <- scholar::get_publications(id)$autho
author <- scholar::get_profile(id)$name
ids <- c("B7vSqZsAAAAJ", "qj74uXkAAAAJ")
df <- compare_scholar_careers(ids)
format_publications("DO5oG40AAAAJ")
id <- get_publications("bg0BZ-QAAAAJ&hl")
impact <- get_journalrank(journals=id$journal)

predict_h_index("TsztyiMAAAAJ&hl")

profile$total_publications

id <- get_publications("TsztyiMAAAAJ&hl")
impact <- get_journalrank(journals=id$journal)


get_journalrank("International Journal of Open Source Software and Processes", max.distance = 0.05)


# install.packages("bibliometrix")
library(bibliometrix)
data(scientometrics, package = "bibliometrixData")

authors <- c("SMALL H", "CHEN DZ")
Hindex(scientometrics, field = "author", elements = authors, sep = ";")$H

data(garfield, package = "bibliometrixData")
indices=Hindex(garfield, field = "author", elements = "GARFIELD E", years=Inf, sep = ";")

data(corentinmaslard, package = "bibliometrixData")
#################### DRAFT ###################

#################### DRAFT to be hinspired about ###################
# https://github.com/jhelvy/jhelvy_quarto/blob/main/_common.R
# https://www.jhelvy.com/research
```
